Hawk-i HPC CLoud Benchmark Tool

### 2012-08-04 docs/dissertation/MSc-coursework.tex
docs

\begin{abstract}
The switch to cloud computing significant advancement in the history of computing.
\end{abstract}

@@

\chapter{Introduction}
Stating the problem and

@@

\section{Cloud Computing}

@@

\subsection{N-Body Methods}
MD, About the dwarf and application types
optimisation, n^2 and nlogn
Communication pattern!!!

@@

{\underline}Discrete Fourier Transform
The discrete Fourier transform of N complex points fk is defined as 
\begin{math}

\end{math}

@@

\chapter{Cluster Computing Setup}
\subsection{Using Starcluster}
\subsection{Cluster Management package}
\subsection{Using Sun Grid Engine}
\subsection{Creating Dashboard}
\chapter{Benchmarking  programs}

\begin{thebibliography}{100}

\bibitem{ref:lam} L.Lamport. {\em 1986 Latex User's Guide
and Reference Manual.} Addison Wesley. pp242.

\bibitem{ref:bloggs} F.Bloggs. {\em 1993 Latex Users do it
in Environments} Int. Journal of Silly Findings. pp 23-29.

\end{thebibliography}

>>>>

\begin{abstract}
Scientific computing unravel the mysteries of science by constructing mathematical models and numerical algorithms. This required massive computational power and High-Performance Computing (HPC) solutions like cluster and grid have been the answer for massive computing to these needs for a long time. These HPC solutions are hard and expensive to setup, maintain and use. \emph{Cloud computing} is a model of delivering the existing compute infrastructure where computation and storage can be dynamically provisioned on a pay as you go model. Using a vendor cloud service like Amazon Web Service (AWS) can significantly reduce the effort to access these on-demand high performance resources.

In this work we create a platform to study how useful Amazon EC2 cloud computing can be for scientific applications. 
We classify the applications based on the concept of computational \emph{motif}\cite{asanovic2008parallel}  
\end{abstract}

@@

\chapter{Introduction}

@@

\section{Cloud Computing}
In 1960 John McCarthy predicted that "computation may someday be organised as a public utility". Availability of high  capacity networks and low cost hardware as well as the adoption of hardware virtualisation technology made this prediction come true. This delivery model enabled a large community of end-users to obtain computing and storage capacity on-demand.

@@

\subsection{N-Body Methods}
MD, About the dwarf and application types optimisation, n2 and nlogn
Communication pattern!!!

@@

{\underline Discrete Fourier Transform}
The discrete Fourier transform of N complex points fk is defined as

@@

\chapter{Cluster Computing Setup}
\subsection{Using Starcluster}
\subsection{Cluster Management package}
\subsection{Using Sun Grid Engine}
\subsection{Creating Dashboard}
\chapter{Benchmarking  programs}
\subsection{Spectral Methods}
\subsection{N-body}

\bibliographystyle{plain}
\bibliography{dissertation}
